---
title: "Class Documents"
output: 
  html_document:
   toc: true
   toc_depth: 3
   toc_float: true
   theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = F, message = F)
```

<br>


Documents from class will be posted on this page.

<br>

# Unit 1
### Introduction 

- [slide]()
- [notebook](https://github.com/loperntu/comsem/blob/master/notebooks/unitl/11.ipynb)
- [math tutorial](https://github.com/loperntu/comsem/blob/master/tutorial/) and [video]()

#### Readings

- [TBA]()




<br>

# Unit 2
### Compositional Semantics and Logical Representation 

- [slide](https://github.com/JSC270/JSC270.github.io/blob/master/notebooks/class2/lecture2_slides_posted2.ipynb)
- [notebook]()
- [math tutorial]() and [video]()

#### Readings

- [TBA]()

<br>

# Unit 3
### Stochastic Semantics

- [slide](https://github.com/JSC270/JSC270.github.io/blob/master/notebooks/class2/lecture2_slides_posted2.ipynb)
- [notebook]()
- [math tutorial]() and [video]()
- Datasets used: [Movies dataset](https://github.com/JSC270/JSC270.github.io/blob/master/notebooks/class3/data/50movies-clean.csv)

#### Readings

- [TBA]()

<br>



# Unit 4 
### Distributed Semantics and Vectorized Representation

- [slide](https://github.com/JSC270/JSC270.github.io/blob/master/notebooks/class2/lecture2_slides_posted2.ipynb)
- [notebook]()
- [math tutorial]() and [video]()
- Datasets used: [Movies dataset](https://github.com/JSC270/JSC270.github.io/blob/master/notebooks/class3/data/50movies-clean.csv)



#### Readings

- [TBA]()


<br>

# Unit 5
### Lexicalized Ontologies and Graphical Representation

- [slide](https://github.com/JSC270/JSC270.github.io/blob/master/notebooks/class2/lecture2_slides_posted2.ipynb)
- [notebook]()
- [math tutorial]() and [video]()

#### Readings

- [TBA]()



<br>

# Unit 6
### Computational Pragmatics and Contextual representation

- [slide](https://github.com/JSC270/JSC270.github.io/blob/master/notebooks/class2/lecture2_slides_posted2.ipynb)
- [notebook]()
- [math tutorial]() and [video]()

#### Readings

- [TBA]()

<br>

# Unit 7
### Reflections of Chinese NLP: a computational functional linguistic view
- [slide](https://github.com/JSC270/JSC270.github.io/blob/master/notebooks/class2/lecture2_slides_posted2.ipynb)
- [notebook]()
- [math tutorial]() and [video]()

#### Readings

- [TBA]()

<br>

# Unit 8
### Multimodal Semantics
- [slide](https://github.com/JSC270/JSC270.github.io/blob/master/notebooks/class2/lecture2_slides_posted2.ipynb)
- [notebook]()
- [math tutorial]() and [video]()

#### Readings

- [TBA]()
<br>

# Unit 9
### Meaning Transformation and Machine Translation

- [slide](https://github.com/JSC270/JSC270.github.io/blob/master/notebooks/class2/lecture2_slides_posted2.ipynb)
- [notebook]()
- [math tutorial]() and [video]()

#### Readings

- [TBA]()

<br>


# Unit 10
### Meaning Generation and NLG

- [slide](https://github.com/JSC270/JSC270.github.io/blob/master/notebooks/class2/lecture2_slides_posted2.ipynb)
- [notebook]()
- [math tutorial]() and [video]()

#### Readings

- [TBA]()
<br>



# Unit 11
### Meaning Disambiguation and WSD

- [slide](https://github.com/JSC270/JSC270.github.io/blob/master/notebooks/class2/lecture2_slides_posted2.ipynb)
- [notebook]()
- [math tutorial]() and [video]()

#### Readings

- [TBA]()

<br>

# Unit 12
### Semantic Inference

- [slide](https://github.com/JSC270/JSC270.github.io/blob/master/notebooks/class2/lecture2_slides_posted2.ipynb)
- [notebook]()
- [math tutorial]() and [video]()

#### Readings

- [TBA]()


******

# Python References


- [seaborn documentation](https://seaborn.pydata.org/)

- [matplotlib documentation](https://matplotlib.org/)

- [pandas documentation](http://pandas.pydata.org/pandas-docs/stable/)



<br>

******

# Class Schedule

```{r, echo=FALSE}
library(tidyverse)
jsc270_classsched <- read_csv("class_schedule.csv", col_types = cols(Week = col_character()), na = "null")
knitr::kable(jsc270_classsched)
```

