---
title: "Class Documents"
output: 
  html_document:
   toc: true
   toc_depth: 3
   toc_float: true
   theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = F, message = F)
```

<br>


Documents from class will be posted on this page.

<br>

# Unit 1
## Introduction 

- [slide](units/1/introduction.pdf)


#### Readings and References

- [Natural Language Processing: 50 years]()
- [Introducing Semantics, Nick Riemer]()

#### Python warmup exercise
   - [notebook]()

<br>

# Unit 2
## Vector Semantics

- Distributional and distributed semantics

   - [slide](),
   - [notebook]()
   - [math tutorial]() and [video]()

- Neural language models

   - [slide]()

- Bias and Meaning

   - [slide]()


#### Lab
   - [notebook]()
   - [assignment.1]()
   - [assignment.2](https://bit.ly/3lB9YsT)

#### Readings

- [JM-SLP-v3, Chapter 6,7,9]()


   
<br>






# Unit 3
## Graph Semantics

- Lexicon and Graphical Representation
   - [slide]()
   - [notebook]()
   - [math tutorial]() and [video]()

- Ontologies
   - [slide]()
   - [notebook]()
   
- Building hybrid knowledge representation from text corpora and knowledge graph
   - [slide]()

#### Readings

- [Introducing Qualia Structure](http://gl-tutorials.org/wp-content/uploads/2015/12/GL-QualiaStructure.pdf)
- [Making AI meaningful again](https://arxiv.org/abs/1901.02918)
- [OntoClean Methodology.tutorial](http://mowl-power.cs.man.ac.uk/2010/comp/owl-60462/OntoClean.pdf)


<br>


# Unit 4
## Meaning and Units


- [slide.1](); [slide.2](units/5/Biemann_vector_or_graph.pdf)
- [notebook]()
- [math tutorial]() and [video]()
- Datasets used: 



#### Readings

- [TBA]()


<br>



# Unit 5
## Meaning Disambiguation and Resolution

- [slide]()
- [notebook]()
- [math tutorial]() and [video]()

#### Readings

- [TBA]()

#### Tasks

- [Word Sense Disambiguation]()
- [Event Co-reference Resolution]()

<br>



# Unit 6 
## Meaning transfer

Computational Pragmatics and Contextual representation

- [slide]()
- [notebook]()

#### Readings

- [TBA]()

<br>

Neural Machine Translation

- [slide]()
- [notebook]()


Diachonic semantic modeling

- [slide]()
- [notebook]()


# Unit 7
## Multimodal Semantics

- [slide]()
- [notebook]()
- [math tutorial]() and [video]()

#### Readings

- [TBA]()
<br>


# Unit 8
## Semantic Inference

- [slide]()
- [notebook]()
- [math tutorial]() and [video]()

#### Readings

- [TBA]()





******

# Class Schedule

```{r, echo=FALSE}
library(tidyverse)
jsc270_classsched <- read_csv("class_schedule.csv", col_types = cols(Week = col_character()), na = "null")
knitr::kable(jsc270_classsched)
```



******

# Python References


- [seaborn documentation](https://seaborn.pydata.org/)

- [matplotlib documentation](https://matplotlib.org/)

- [pandas documentation](http://pandas.pydata.org/pandas-docs/stable/)



<br>


