---
title: "Class Documents"
output: 
  html_document:
   toc: true
   toc_depth: 3
   toc_float: true
   theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = F, message = F)
```

<br>


Documents from class will be posted on this page.

<br>

# Unit 1
### Introduction 

- [slide]()
- [notebook](https://github.com/loperntu/comsem/blob/master/notebooks/unitl/11.ipynb)
- [math tutorial](https://github.com/loperntu/comsem/blob/master/tutorial/) and [video]()

#### Readings

- [TBA]()




<br>

# Unit 2
### Compositional Semantics and Logical Representation 

- [slide]()
- [notebook]()
- [math tutorial]() and [video]()

#### Readings

- [TBA]()

<br>






# Unit 3
### Lexicalized Ontologies and Graphical Representation

- [slide]()
- [notebook]()
- [math tutorial]() and [video]()

#### Readings

- [Introducing Qualia Structure](http://gl-tutorials.org/wp-content/uploads/2015/12/GL-QualiaStructure.pdf)
- [Making AI meaningful again](https://arxiv.org/abs/1901.02918)



<br>


# Unit 4
### Stochastic Semantics

- [slide]()
- [notebook]()
- [math tutorial]() and [video]()
- Datasets used: 

#### Readings

- [Bayesian network]()

<br>





# Unit 5
### Distributed Semantics and Vectorized Representation

- [slide.1](); [slide.2](units/5/Biemann_vector_or_graph.pdf)
- [notebook]()
- [math tutorial]() and [video]()
- Datasets used: 



#### Readings

- [TBA]()


<br>




# Unit 6
### Computational Pragmatics and Contextual representation

- [slide]()
- [notebook]()
- [math tutorial]() and [video]()

#### Readings

- [TBA]()

<br>

# Unit 7
### Reflections of Chinese NLP: a computational functional linguistic view
- [slide]()
- [notebook]()
- [math tutorial]() and [video]()

#### Readings

- [TBA]()

<br>

# Unit 8
### Multimodal Semantics
- [slide]()
- [notebook]()
- [math tutorial]() and [video]()

#### Readings

- [TBA]()
<br>

# Unit 9
### Meaning Transformation

- [slide]()
- [notebook]()
- [math tutorial]() and [video]()

#### Readings

- [TBA]()

#### Tasks

- [Machine Translation]()


<br>


# Unit 10
### Meaning Generation and NLG

- [slide]()
- [notebook]()
- [math tutorial]() and [video]()

#### Readings

- [TBA]()
<br>



# Unit 11
### Meaning Disambiguation and Resolution

- [slide]()
- [notebook]()
- [math tutorial]() and [video]()

#### Readings

- [TBA]()

#### Tasks

- [Word Sense Disambiguation]()
- [Event Co-reference Resolution]()

<br>

# Unit 12
### Semantic Inference

- [slide]()
- [notebook]()
- [math tutorial]() and [video]()

#### Readings

- [TBA]()


******

# Class Schedule

```{r, echo=FALSE}
library(tidyverse)
jsc270_classsched <- read_csv("class_schedule.csv", col_types = cols(Week = col_character()), na = "null")
knitr::kable(jsc270_classsched)
```



******

# Python References


- [seaborn documentation](https://seaborn.pydata.org/)

- [matplotlib documentation](https://matplotlib.org/)

- [pandas documentation](http://pandas.pydata.org/pandas-docs/stable/)



<br>


